\documentclass{article}

\usepackage{graphicx} 

\input{tex_files/preamble}

\addbibresource{tex_files/sample.bib}

\input{tex_files/title}

\begin{document}
\maketitle

% Does the first line need to be toned down?
% People seem to be making these sorts of society-changing claims.
\begin{abstract}
  Artificial Intelligence, in particular generative AI (gen-AI) and Large Language Models (LLMs), have engaged the public in ways that mirror other critical advances in computing technologies like the PC and smartphone revolutions of the 1980s and 2000s, and the rapid expansion of the Internet over the past three decades. Entire industries, including education, are simultaneously attempting to predict and shape the future directions of these and related technologies.

  While Machine Learning (ML) technologies like LLMs have a profound capacity to integrate AI techniques into modern life, work, and society, the underlying technologies such as Artificial Neural Networks (ANNs) have presented serious issues concerning both short and long-term sustainability. These issues come in a number of forms: footprint for data centers, waste artifacts such as heat and noise, and they require a rather significant footprint regarding precious resources such as energy (infrastructure) and clean water for cooling.

  At the same time, advanced declarative languages have made remarkable headway towards generalized AI solutions that are designed with efficiency in mind. In particular, Answer Set Programming (ASP) languages are designed to solve computationally difficult (NP-Complete and NP-Hard) with limited available resources. We hope that by merging technologies from other areas of AI, like ASP languages and solvers, that we may be able to accelerate the learning and inference processes for ANNs, thereby creating a more sustainable computing environment as these technologies continue to explode in their growth.

  In this paper we discuss our work creating a representation for ANNs in the ASP dialect of Clingo. As an example domain, we use the widely-studied area of digital logic for hardware construction. We also introduce C-MCPN: The Clingo McCulloch-Pitts Network Editor. C-MCPH is a utility written in Python to assist in our research, and serves as a lightweight, graphical Integrated Development Environment (IDE) for developing these digital-logic based ANNs, including the ability to specify more general neuron structure and activation outside of logical gates. 
\end{abstract}

\input{tex_files/sections/introduction}
\input{tex_files/sections/background}
\input{tex_files/sections/methodology}
\input{tex_files/sections/implementation}
\input{tex_files/sections/results}
\input{tex_files/sections/conclusion}

\medskip

\printbibliography

\end{document}
