\section{Introduction}

Artificial Intelligence systems have had a significant impact on the modern world over the decades. Some of the many advancements across various fields include (however certainly not limited to) conversational agents, marketing, medicine, and insurance \parencite{Nossig2024}. Historically many of these advances and their impact on shaping the modern world have occurred in the background, improving our systems and applications iteratively and often at the periphery of the thinking of the general public. With new advances in AI like machine learning methods (ML) and generative AI (in particular Large Language Models or LLMs), these systems have come to the forefront of public consciousness in a way that is likely to remain for the foreseeable future.

While these AI systems have the potential for significant advancement, a number of contemporary models come with significant drawbacks. In particular, the necessary growth of AI data centers and their associated infrastructure needs have caused significant stress for many local populations \parencite{Implications2025}. These issues are leading to worsening availability of resources for the general public, and lead directly to the potential of significant environmental and health impacts \parencite{Han2025}.

For continued advancement to avoid outpacing our environmental needs, significant research is necessary to bring down their respective footprints. Artificial Neural Network (ANN) technologies have made many of these technological advances possible, however drawbacks concerning their efficiency are a continued cause for concern regarding overall sustainability \parencite{DeVries2023}.

Answer Set Programming (ASP) languages often live at a different end of the research spectrum. These languages are designed to solve NP-Complete and NP-Hard problems in a way that is fast and efficient. In this paper we conduct investigate how to merge these schools of thought by building, representing, and performing inference over ANNs, specifically McCulloch-Pitts Networks (MPNs) \parencite{McCulloch1943}. To this end we introduce {\tt C-MCPN}: The \emph{Clingo McCullouch-Pitts Network Editor}.

In this paper we will introduce basic techniques for modeling ANNs in the ASP language Clingo, and demonstrate how {\tt C-MCPN} can be used to operate over ANN models.

