\section{Results}

The results of this work is the C-MCPN Framework and Editor, which provide a novel approach to representing and working with logical networks within the paradigm of logic programming. The framework and included neuron gates were validated for correctness using an 8-bit adder network, and the editor was used to construct and visualize this network. While being the main motivation for this work, results on its efficiency and scalability are left for future work since that will matter more for the adaptive neural network framework we are currently developing. The C-MCPN Framework and Editor are both open source and available at \url{https://github.com/*********}.

\subsection{Limitations}

This work is a proof of concept for building ANNs in Clingo, and as such there are some limitations to be aware of. The framework has no cycle detection nor has it been tested on recurrent networks. This is likely to cause issues with the value inference program, as it relies on the values being propagated along the edges. The framework has also not been tested on large networks, and it is unknown how scale will affect its performance. Also, as noted in Section \ref{methodology}, Clingo does not have native support for floating point numbers, limiting its potential applications. 

\subsection{Future Work}

While there are many potential avenues for future work in this area, we are most excited about the possibility of using the C-MCPN Framework as the skeleton for an adaptive neural network which can learn on data. This framework is in its early stages, but we hope to also add it as a feature in the C-MCPN Editor in the future.
